Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-10 docs/ms.tex
Update ms.tex

A typical procedure of weak lensing analysis  includes galaxy shape measurements from images
,shear inference and mass profile reconstruction. The galaxy shape measurement is usually the
first step of weak lensing analysis, since it's a direct observable of shear effect. However
in this paper we only concern about how to infer shear from galaxy
ellipticity in a novel hierarchical way. Therefore we set up a simple toy model in which we have the observed ellipticity as
data, and the only shape measurement error we consider is a Gaussian noise
added on the lensed galaxy ellipticity. We also suppose there is a uniform shear
acting on all the galaxies in one sky patch.

@@

In galaxy--galaxy lensing, since the distortion is so weak, what people
usually do is to stack many lensing signals together. Then they can the mean
shear map and infer the mean mass profile of single galaxy or galaxy
cluster. However with the Hierarchical Bayesian method we can avoid this brute averaging
of lensing signal. Instead, we can get the posterior distribution of mass profile for
each lensing system, even though it may have very large uncertainty. Then we
can calculate their statistical properties like galaxy-mass correlation
function via this posterior distribution.

>>>>

A typical procedure of weak lensing analysis  includes galaxy shape measurements from images
, shear inference and mass profile reconstruction. The galaxy shape measurement is usually the
first step of weak lensing analysis, since it's a direct observable of shear effect. However
in this paper we only concern about how to infer shear from galaxy
ellipticity in a novel hierarchical way. Therefore we set up a simple toy model in which we have the observed ellipticity as
data, and the only shape measurement error we consider is a Gaussian noise
added on the lensed galaxy ellipticity. We also suppose there is a uniform shear
acting on all the galaxies in one sky patch.

@@

In galaxy--galaxy lensing, since the distortion is so weak, what people
usually do is to stack many lensing signals together. Then they can obain the mean
shear map and infer the mean mass profile of single galaxy or galaxy
cluster. However with the Hierarchical Bayesian method we can avoid this brute averaging
of lensing signal. Instead, we can get the posterior distribution of mass profile for
each lensing system, even though it may have very large uncertainty. Then we
can calculate their statistical properties like galaxy-mass correlation
function via this posterior distribution.
